SAT Competition 2020\tnoteref{title}

### 2020-12-15 paper/main.tex
indicated all maple-forks; prepared icons

TODO: maybe mention \url{https://satcompetition.github.io/2020/}

TODO: Maybe mention proceedings \cite{SC2020}

@@

@@

@@

\subsection{Rules, ranking, etc.}

DRAT checking; cake\_lpr\_array

@@

TODO: Incremental / Parallel / Cloud ?

@@

@@

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{MapleLCMDistCBT} & padc\_dl & \\
 &  & padc\_dl\_ovau\_lin & \\
 &  & padc\_dl\_ovau\_exp & \\
 &  & psids\_dl & \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & DurianSat & -- & \\
\hline

@@

Riveros & SLIME & -- & \\
\hline

@@

Kaiser, Hartung & PauSat & -- & \\
\hline

@@

\subsection{Parallel Track}

@@

The authors of ManyGlucose received two awards in this competition. 
ManyGlucose was submitted in 32-core and 64-core variants~\cite{}.
The 32-core variant won third prices in the overall evaluation and in the unsat sub-track. 
ManyGlucose is a fork of GlucoseSyrup~\cite{} and uses strategies similar to those known from ManySAT~\cite{} in order to achive deterministic solver runs.

@@

\subsection{Cloud Track}

@@

@@

@@

>>>>

\todo{maybe mention \url{https://satcompetition.github.io/2020/}}

\todo{Maybe mention proceedings \cite{SC2020}}

@@

SAT Competition 2020 consisted of four tracks, 
the Main track, Incremental Library track, Parallel track,
and the Cloud Track for massively parallel SAT solvers using up to 1024 cores.

@@

\todo{Did we have a glucose hack track in the end?
(Mentioned on the web, not in the result slides.)}

@@

\subsection{Mandatory participation requirements}

\todo{Should we have a discussion (maybe later sections)
about the future of the portfolio solver rule
concerning the point raised by Mate Soos (in emails)?}

\subsection{Certificates}

In all tracks it was required to output a model to certify recognising a satisfiable instance.
On the other hand, certificates for unsatisfiable instances (proofs) were required only 
in the Main Track (besides the No Limits subtrack).

Proofs of unsatisfiability were to be emitted in the DRAT format~\cite{DRATtrim},
either in its textual version, which is very similar to the DIMACS input format,
or on a more compact binary version (for more details, see \cite{satComp2020www}, Unsat Certificates).

The proofs were validated in a two step fashion. First, the tool {\tt DRAT-trim}~\cite{DRATtrim}
was used for initial checking and optimizing the emitted proof, deriving a so-called LRAT proof file.
Afterwards, an independent, formally-verified checker {\tt cake\_lpr} \cite{cakeLprGithub}, 
was used for validating the LRAT proof as a correct proof of unsatisfiability of the given formula.
We only considered solved those unsatisfiable formulas that could be validated by {\tt DRAT-trim}.
There were several cases where {\tt cake\_lpr} ran out of resources before being able to 
confirm after {\tt DRAT-trim}. However, there was no case where {\tt DRAT-trim} would accept
a proof and {\tt cake\_lpr} would later disagree with the verdict.

@@

The Incremental Library Track was run on computers with 2x Intel Xeon E5430 \SI{2.66}{\giga\hertz}
(4-Core) processors and \SI{24}{\giga\byte} of RAM.

\todo{Parallel / Cloud}

@@

\todo{New Codebases}

@@

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{ExMapleLCMDistCBT} & padc\_dl & \\
 &  & padc\_dl\_ovau\_lin & \\
 &  & padc\_dl\_ovau\_exp & \\
 &  & psids\_dl & \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & MapleLCMDistCBT-DL-v3 & DurianSat & \\
\hline

@@

Riveros & MapleLCMDistCBT & SLIME & \\
\hline

@@

Kaiser, Hartung & MapleLCMDist & PauSat & \\
\hline

@@

\subsection{Parallel SAT Solving: Winners of the Parallel Track}

@@

The authors of ManyGlucose received two awards in this competition. 
ManyGlucose was submitted in 32-core and 64-core variants~\cite{}.
The 32-core variant won two third prices, one in the overall evaluation and one in the unsat sub-track. 
ManyGlucose is a fork of GlucoseSyrup~\cite{} and uses strategies similar to those known from ManySAT~\cite{} in order to achive deterministic solver runs.

@@

\subsection{Massively Parallel SAT Solving: Winners of the Cloud Track}

@@

The massively parallel SAT solver Mallob is based on HordeSAT~\cite{}. 
Mallob is a framework for massivley parallel and distributed \emph{malleable job scheduling}, and thus can perform dynamic load balancing on many jobs of varying priorty.
However, in the submitted version Mallob Mono, this functionality is disabled, as traditionally in SAT Competition all resources are busy solving one single instance only.

Mallob uses the the 2018 version \emph{bcj} of Lingeling~\cite{} and employs diversification via randomized sparse initialization of branching scores just like it is done in Plingeling~\cite{}. 
Every 14th process, however, runs the local search solver YalSAT~\cite{}.

Clause exchange is handled considerably different from previous approach. 
Workers are organized in a binary tree and clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
Each node performs a three way merge of the local and the two incoming buffers. 
Only the final aggragate at the root of that binary tree is broadcast to all the solvers.

To limit sharing, there is a global size limit of $5$ for all the shared clauses. 
The buffer has a limited size as well, but that size depends on the position in the binary tree, with root having the largest buffer and leaves the smallest. 
Clauses are sorted by there size during aggregation, such that smaller clauses are preferred over longer clauses. 
Duplicates are filtered out using a bloom filter, which is cleared periodically. 
There is a special filter for duplicate unit-clause which especially useful during startup.

@@

TopoSAT~2 is a massively parallel SAT solver using Glucose~3 with lockfree clause-exchange as in ManySAT~\cite{} on each node, and using MPI to share clauses between nodes.

In Toposat~2, diversification is done via different strategies used for branching, restarting and clause forgetting. 
Clauses are strengthened before they are exported. 
Locally, clause import is delayed until the local trail-size is low in a monitored period.

@@

Slime is build on top of MapleLCMDistChronoBT and was first submitted to SAT Race 2019 suggesting the new phase selection heuristic~\cite{}. 
The 2020 version apparently adds some kind of periodic randomization in geometrically increasing intervals~\cite{}. 
Even thought the sequential solver was unsuccessful in the Main Track, its MPI-based cloud version, won the third price in this competitions cloud track.
